\subsubsection{Brief introduction to COCOMO II}
TODO

\subsubsection{Scale Factors}
\paragraph*{Precedentedness: Low}
We have never built any similar application, although the structure of the application is not different from other projects that we have worked on.

\paragraph*{Development Flexibility: High}
Management did not impose a choice of framework, architecture or any set of constraints except the product goals.

\paragraph*{Architecture/Risk Resolution: Low}
We were not provided with little information about risk management, budget and architecture, and had to work it out ourselves.

\paragraph*{Team Cohesion: High}
We had a couple of small misunderstandings early on, but managed to work them out and have been efficiently working together.

\paragraph*{Process Maturity: Nominal}
We believe the CMMI level to be around "Defined", accounting for our relative lack of experience but proactive attitude.

\subsubsection{Post-architecture Cost Drivers}
\paragraph*{Required Software Reliability: Nominal}
A service malfunction could cause inconvenience and non-trivial financial losses.

\paragraph*{Data Base Size: Nominal}
The database size is standard for a medium-to-small-sized application. The database mainly stores data about Cars, Users, and Parking Areas.

\paragraph*{Product Complexity: Nominal}
The product's complexity is par for the course for a medium-to-small-sized application.

\paragraph*{Developed for Reusability: Nominal}
There was no specific reusability requirement, but we made the application modular, so to allow for future expansion and modification.

\paragraph*{Documentation Match to Lifecycle Needs: Nominal}
Adequately-sized documentation is provided for the various stages of the project.

\paragraph*{Analyst Capability: Nominal}
We believe our skills to be around average, accounting for our relative lack of work experience.

\paragraph*{Programmer Capability: Nominal}
We believe our skills to be around average, accounting for our relative lack of work experience.

\paragraph*{Personnel Continuity: Very High}
The three of us kept working on the project from beginning to end.

\paragraph*{Application Experience: Low}
We have little experience in developing complete applications.

\paragraph*{Platform Experience: Low}
We have little experience working with Spring, Tomcat and nginx.

\paragraph*{Language and Toolset Exerience: Nominal}
We have a good undersdtanding of Java, if a somewhat limited experience.

\paragraph*{Time Constraint: Very High}
Rapid communication between the Cars, the User Application and the Central Service is essential for good software performance.

\paragraph*{Storage Constraint: Nominal}
No specific storage constraint was mentioned, and the amount of data created by the application is modest in size.

\paragraph*{Platform Volatility: Low}
No major or major changes to the project were communicated.

\paragraph*{Use of Software Tools: High}
During development, several strong tools would be used to check on the lifecycle, such as mantaining a git repository.

\paragraph*{Multisite Development: Extra High}
Most of the work was done from home, coordinating through IRC.

\paragraph*{Required Development Schedule: Nominal}
A rigid schedule was imposed on us for the first documents (RASD and DD), but we had more freedom for the project development.

\subsubsection{Effort Calculation}

\subsubsection{Scheduling}

\subsubsection{Team Dimensions}