\subsection{Possible risks}

\begin{tabular}{|p{.07\textwidth}|p{.23\textwidth}|p{.4\textwidth}|l|l|}
\hline
\textbf{Code} & \textbf{Name} & \textbf{Description} & \textbf{Chance} & \textbf{Impact} \\ \hline
R01 & New competitors & A different company starts its own analogous service, so that our service is no longer needed. & Low & Serious \\ \hline
R02 & Client's abandonment & Client withdraws interest and funding, stopping development before release. & Medium & Critical \\ \hline
R03 & Lack of Budget & The allocated budget is insufficient to ensure development within schedule. & Medium & Serious \\ \hline
R04 & Client's modifications & Client decides to change some significant detail of the application during development. & Medium & Marginal \\ \hline
R05 & Customer's unforeseen needs & Customers need some feature that wasn't planned and included in the RASD. & High & Marginal \\ \hline
R06 & Car-Mobile communication failure & Cars and Mobile applications can't communicate properly with the Central Server. & Medium & Serious \\ \hline
R07 & Database failure & The Database is prone to errors, causing data to be unavailable or lost. & Low & Marginal \\ \hline
R08 & Server failure & The Server is prone to problems, blocking the whole system. & Medium & Serious \\ \hline
R09 & Developer's inability to work & Because of illness, personal problems or such, some of the developers can't work on the project any longer. & Medium & Critical \\ \hline
\end{tabular}

\clearpage
\subsection{Preventive strategies}
\begin{description}
	\item[R01] An accurate market analysis has to be filled out by the Client before choosing to set the project up. We can't be held responsible for the needs of the market shifting.
	\item[R02] We will require a forward payment as well as a fee for early termination.
	\item[R03] We will need to provide a realistic estimation of budget. We will need to specify in the contract that a reduction in budget will result in a sub-par product or a longer development time.
	\item[R04] We will change the product according to the Client's desires. However, we'll calculate the workload needed for these changes and warn them of the consequent increase in development time and cost.
	\item[R05] This is a problem concerning Requirement Engineering. We will set up the system so as to make it easy to expand its functionalities to accomodate any unforeseen needs.
	\item[R06] We will have to invest time and effort towards having the hardware and software needed for communication working at top performance during development. We will document extensively that area in case modifications are needed.
	\item[R07] The DBMS is external. We recommend keeping a redundant backup database in order to be able to restore functionality immediately.
	\item[R08] We will build the Server systems for parallelism, in order to minimize the consequences of a crash. Also, we'll write instructions on how to fix Server problems for the Company's IT department.
	\item[R09] We will keep some talented replacements for the missing developer(s). However, even in the best case scenario, this will extend the development time because of communications overhead.
\end{description}