\subsection{External Interface Requirements}
%TODO I would avoid to include here the interfaces of the base software (operating system, web server, etc) for your system. Focus instead on the external software your system is going to interact with (e.g., the payment gateway you mentioned)
This system provides a detailed description of all inputs into and outputs from the system. It also gives a general description of the hardware, software and communication interfaces.

\subsubsection{Hardware Interface}
Reliable software device drivers shall be provided for the Car Boards used by the System. They should be completely tested to prove the full access to the Car prebuilt devices and the correct communication with the Backend. 
The Areas information coming from the Areas sensors should also be reachable from the System in order to get the number of free parking and/or charging slots. The communication with this sensors should be completely tested to prove the full access of the Backend to this data.
The Application should be able to connect to the GPS module of the Device. It should be completely tested to prove the full access to this module. 

\subsubsection{Software Interface}
The Application has to communicate with the Mapping System in order to display maps and to get a GPS position given a street address.

The Backend has to communicate with the following systems:
\begin{itemize}
	\item Mailing System. It has to provide an API to send send mails to the Users. 
	\item Banking System. It has to provide an API to charge credit cards of a specific amount of money.
	\item Company. It has to provide an API to send notifications and messages.
	\item Cars. They have to provide full access to the set of sensors needed by the System.
	\item Company Database. It has to provide a way to reach the System Database hosted on the Company Database infrastructure.
\end{itemize}

\subsubsection{User Interface}
The Application is the only interface between a Visitor or an User and the System.

A generic Visitor of the Application should only see the registration and login forms. If the Visitor has not registered yet, he/she should be able to do it through the registration form. On the other hand, if the Visitor is already registered, he/she should be able to log in through the login form.

Whenever a Visitor logs in into the System through the Application, he/she becomes a User and can access all the functionalities of the System reserved to him/her.

Every User use the Application to :
\begin{itemize}
	\item communicate to the System his/her GPS position and visualize it on a map
	\item locate all the Cars Available in a range of 5 km from his/her GPS position or from a given address and visualize them on a map
	\item reserve a Car among the one previously displayed
	\item unlock a Car when he/she is nearby the previously reserved Car
	\item know if a Car is plugged to a socket of a Charging Area
	\item know the Battery status of a Car
	\item know the GPS position of Charging Area and Parking Area and visualize it on a map	
	\item select the \textit{Money saving option}
\end{itemize}

The Application also communicate to the User short error messages.

\subsubsection{Communication Interface}
As already mentioned, the System heavily uses Internet Protocol Suite protocols, mainly the HTTP(S) protocol, in order to communicate with all its components.