\documentclass{article}

\usepackage{enumitem}

\begin{document}

\begin{enumerate}[label=R\arabic*]
\item PowerEnjoy shall provide Users with the ability to access all the System functionalities reserved to them.
\item PowerEnjoy shall support Users in locating Available Cars within a range of 5 Km from a specific position.
\item PowerEnjoy shall support Users in locating Parking Areas and their free parking slots.
\item PowerEnjoy shall support Users in locating Charging Areas and their free parking and charging slots.
\item PowerEnjoy shall support Users in reserve Available Cars.
\item PowerEnjoy shall have a timer to know how much time passed since a User made a reservation.
\item PowerEnjoy shall support a User in unlock a Car he/she has previously reserved when he/she is in a range of 15 meters from the same Car.
\item PowerEnjoy shall support Users in driving Cars previously unlocked by them.
\item PowerEnjoy shall have a timer to know how much time passed since a User is driving a Car.
\item PowerEnjoy shall allow the User to end the ride in a Parking or Charging Area.
\item PowerEnjoy shall interface with an external Mailing System to send emails to Users.
\item PowerEnjoy shall interface with an external Banking System to charge the Users.
\item PowerEnjoy shall interface with an external GPS System to know the positions of Users and Areas.
\item PowerEnjoy shall interface with an external Mapping System to know the positions of Users and Areas.
\item PowerEnjoy shall interface with the existing Car to get their GPS position, damages, connection to an electrical socket, the number of seats occupied.
\item 
\end{enumerate}

\end{document}